Consumption and resistance across states and HRRs

### 2017-02-28 states/resistance/state-report.Rmd
refactored

# get all bug/drug combos (i.e., all bug/cons drug combos with appropriate res drugs)
bug_drug = expand.grid(bug=organisms,
                       consumption_drug=consumption_drugs,
                       stringsAsFactors=FALSE) %>%
  left_join(consumption_resistance, by='consumption_drug') %>%
  select(bug, consumption_drug, resistance_drug)
```

@@

### Geography-averaged results

@@

#### State-level geography-averaged correlations

```{r state_average_results_table}
results %>%
  filter(place=='state') %>%
  mutate_if(is.numeric, function(x) signif(x, digits=3)) %>%
  select(bug, consumption_drug,
         coherent, explanatory, correlation,
         adj.p.value, sig,
         plot_link) %>%
  kable
```

There correlations are mostly positive, but only a small number are significant (red line marks $p = 0.05$):

```{r state_average_histogram}
result %>%
  filter(place=='state') %>%
  ggplot(aes(x=correlation, y=adj.p.value)) +
  geom_point() +
  geom_hline(yintercept=0.05, col='red') +
  xlab('correlation coefficient') + ylab('p value (reversed)') +
  scale_y_reverse() +
  theme_minimal()
```

### HRR

```{r}
hrr_res %>%
  mutate_if(is.numeric, function(x) signif(x, digits=3)) %>%
  select(bug, consumption_drug,
         hrr_coherent, explanatory, correlation,
         adj.p.value, sig,
         plot_link) %>%
  kable
```

### Coherent state

@@

```{r display_coherent_result}
coherent_state_res %>%
  mutate_if(is.numeric, function(x) signif(x, digits=3)) %>%
  select(bug, consumption_drug,
     explanatory, correlation,
     adj.p.value, sig,
     plot_link) %>%
  kable
```

### Coherent results from the HRR level

```{r}
coherent_hrr_res %>%
  mutate_if(is.numeric, function(x) signif(x, digits=3)) %>%
  select(bug, consumption_drug,
     explanatory, correlation,
     adj.p.value, sig,
     plot_link) %>%
  kable
```

### State, all points

And I try the same thing again, but this time keeping all the data points:

```{r correlations_with_all_points}
state_dat %>%
  mutate_at(vars(cpkp, did), function(x) if_else(is.na(x), 0, x)) %>%
  group_by(bug, resistance_drug, consumption_drug) %>%
  do(models(., 'percent_susceptible')) %>%
  ungroup %>%
  left_join(coherence, by=c('bug', 'resistance_drug')) %>%
  filter(!is.na(estimate), hrr_coherent) %>%
  mutate(adj.p.value=p.adjust(p.value, method='BH'),
         sig=pvalue_stars(adj.p.value)) %>%
  select(bug, consumption_drug, resistance_drug,
         explanatory, correlation=estimate, p.value,
         adj.p.value, sig) %>%
  mutate_if(is.numeric, function(x) signif(x, digits=3)) %>%
  kable
```

### HRR, all points

```{r}
hrr_dat %>%
  mutate_at(vars(cpkp, did), function(x) if_else(is.na(x), 0, x)) %>%
  group_by(bug, resistance_drug, consumption_drug) %>%
  do(models(., 'percent_susceptible')) %>%
  ungroup %>%
  left_join(coherence, by=c('bug', 'resistance_drug')) %>%
  filter(!is.na(estimate), state_coherent) %>%
  mutate(adj.p.value=p.adjust(p.value, method='BH'),
         sig=pvalue_stars(adj.p.value)) %>%
  select(bug, consumption_drug, resistance_drug,
         explanatory, correlation=estimate, p.value,
         adj.p.value, sig) %>%
  mutate_if(is.numeric, function(x) signif(x, digits=3)) %>%
  kable
```

>>>>

# get all bug/drug combos (i.e., all bug/cons drug combos with appropriate res drugs)
bug_drug = expand.grid(bug=organisms,
                       consumption_drug=consumption_drugs,
                       stringsAsFactors=FALSE) %>%
  as_data_frame() %>%
  left_join(consumption_resistance, by='consumption_drug') %>%
  select(bug, consumption_drug, resistance_drug)
```

@@

### All resistance-averaged results

@@

#### All state-level averaged-resistance correlations

```{r state_average_results_table}
result %>%
  filter(place=='state') %>%
  mutate_if(is.numeric, function(x) signif(x, digits=3)) %>%
  select(bug, consumption_drug,
         coherent, explanatory, correlation,
         adj.p.value, sig,
         plot_link) %>%
  kable
```

There correlations are mostly positive, but only a small number are significant (red line marks $p = 0.05$). The significant negative correlation is for MRSA and TMP-SMX.

```{r state_average_volcano}
result %>%
  filter(place=='state') %>%
  ggplot(aes(x=correlation, y=adj.p.value)) +
  geom_point() +
  geom_hline(yintercept=0.05, col='red') +
  xlab('correlation coefficient') + ylab('p value (reversed)') +
  scale_y_reverse() +
  theme_minimal()
```

#### All HRR-level averaged-resistance

```{r hrr_average_results_table}
result %>%
  filter(place=='hrr') %>%
  mutate_if(is.numeric, function(x) signif(x, digits=3)) %>%
  select(bug, consumption_drug,
         coherent, explanatory, correlation,
         adj.p.value, sig,
         plot_link) %>%
  kable
```

Like with the state-level data, only a small number are significant (red line marks $p = 0.05$), but the correlations seem more split positive and negative.

```{r hrr_average_histogram}
result %>%
  filter(place=='hrr') %>%
  ggplot(aes(x=correlation, y=adj.p.value)) +
  geom_point() +
  geom_hline(yintercept=0.05, col='red') +
  xlab('correlation coefficient') + ylab('p value (reversed)') +
  scale_y_reverse() +
  theme_minimal()
```

The results from the HRR level differ: both identified a relationship between *E. coli* and cipro and MSSA and azithromycin. However, the state-level data  identified a negative relationship between MRSA and Bactrim while the HRR data identified a negative relationship between *K. pneumoniae* and Bactrim. The state-level data also identified *S. pneumoniae* and azithromycin.

### Coherent resistance-averaged

@@

The plots (in the links) here are the same as before. They're actually showing all the data. I should probably have plots that show just the averaged points.

#### Coherent state-level averaged-resistance correlations

```{r coherent_state_average_results_table}
result %>%
  filter(place=='state', coherent) %>%
  mutate_if(is.numeric, function(x) signif(x, digits=3)) %>%
  select(bug, consumption_drug,
         explanatory, correlation,
         coherent.adj.p.value, coherent.sig,
         plot_link) %>%
  kable
```

There correlations are mostly positive, and one or two more are significant (red line marks $p = 0.05$):

```{r coherent_state_average_histogram}
result %>%
  filter(place=='state', coherent) %>%
  ggplot(aes(x=correlation, y=coherent.adj.p.value)) +
  geom_point() +
  geom_hline(yintercept=0.05, col='red') +
  xlab('correlation coefficient') + ylab('p value (reversed)') +
  scale_y_reverse() +
  theme_minimal()
```

#### All HRR-level averaged-resistance

```{r coherent_hrr_average_results_table}
result %>%
  filter(place=='hrr', coherent) %>%
  mutate_if(is.numeric, function(x) signif(x, digits=3)) %>%
  select(bug, consumption_drug,
         explanatory, correlation,
         coherent.adj.p.value, coherent.sig,
         plot_link) %>%
  kable
```

```{r coherent_hrr_average_histogram}
result %>%
  filter(place=='hrr', coherent) %>%
  ggplot(aes(x=correlation, y=coherent.adj.p.value)) +
  geom_point() +
  geom_hline(yintercept=0.05, col='red') +
  xlab('correlation coefficient') + ylab('p value (reversed)') +
  scale_y_reverse() +
  theme_minimal()
```

### All bug/drug, all-antibiogram results

In these data, I don't average the resistance before running the correlation, but I do associate each antibiogram with the same geography-wide consumption.

```{r}
all_models_result = function(x, this_place, consumption) {
  result = x %>%
    mutate_at(vars(cpkp, did), function(x) if_else(is.na(x), 0, x)) %>%
    group_by(bug, resistance_drug, consumption_drug) %>%
    do(models(., 'percent_nonsusceptible')) %>%
    ungroup %>%
    filter(!is.na(estimate)) %>%
    mutate(adj.p.value=p.adjust(p.value, method='BH'),
           sig=pvalue_stars(adj.p.value)) %>%
    left_join(filter(coherence, place==this_place), by=c('bug', 'resistance_drug')) %>%
    select(bug, consumption_drug, resistance_drug, coherent,
           explanatory, correlation=estimate, p.value,
           adj.p.value, sig)

all_state_res = all_models_result(state_dat, 'state', state_consumption)
all_hrr_res = all_models_result(hrr_dat, 'hrr', hrr_consumption)

all_result = bind_rows(
  all_state_res %>% mutate(place='state'),
  all_hrr_res %>% mutate(place='hrr')
)
```

#### All bug/drug, state-wide consumption, all-antibiogram

```{r}
all_result %>%
  filter(place=='state') %>% 
  mutate_if(is.numeric, function(x) signif(x, digits=3)) %>%
  select(bug, consumption_drug, 
         explanatory, correlation, p.value,
         adj.p.value, sig) %>%
  kable
```

#### All bug/drug, HRR-wide consumption, all-antibiogram

```{r}
all_result %>%
  filter(place=='hrr') %>% 
  mutate_if(is.numeric, function(x) signif(x, digits=3)) %>%
  select(bug, consumption_drug, 
         explanatory, correlation, p.value,
         adj.p.value, sig) %>%
  kable
```

#### Coherent, state-wide consumption, all-antibiogram

```{r}
all_result %>%
  filter(place=='state', coherent) %>%
  mutate_if(is.numeric, function(x) signif(x, digits=3)) %>%
  select(bug, consumption_drug,
         explanatory, correlation,
         coherent.adj.p.value, coherent.sig) %>%
  kable
```

```{r}
all_result %>%
  filter(place=='state', coherent, explanatory=='cpkp') %>%
  ggplot(aes(x=correlation, y=coherent.adj.p.value)) +
  geom_point() +
  geom_abline(yintercept=0.05, col='red') +
  scale_y_reverse() +
  theme_minimal()
```

#### Coherent, HRR-wide consumption, all-antibiogram

```{r}
all_result %>%
  filter(place=='hrr', coherent) %>%
  mutate_if(is.numeric, function(x) signif(x, digits=3)) %>%
  select(bug, consumption_drug,
         explanatory, correlation,
         coherent.adj.p.value, coherent.sig) %>%
  kable
```
